---
title: "Event Plotting - AQUACAT"
author: "UKCEH; Adam Griffin"
date: "05/03/2020; updated 10/03/2020"
output:
  html_document: default
  pdf_document: default
---

This document investigates the different number and size of widespread events for different grid-cell threshold and inundation limits. This analysis is based on a 30-year "present-day" period of G2G outputs across Great Britain.

Outputs: "/exampleevent_DAY_INUN.png" plots

```{r setup, echo=F, message=F, warnings=F, errors=F}
library(ncdf4)
library(raster)
library(knitr)
library(kableExtra)
library(dplyr)
library(fields)
library(readr)

threshVal <- c(5/365, 2/365, 1/365, 0.2/365, 0.1/365)
threshName <- c("POT5", "POT2", "POT1", "Q5", "Q10")
NT <- length(threshVal)
```

# Data used and produced in previous scripts
```{r data}

if(substr(osVersion,1,3) == "Win"){
  source("S:/CodeABG/setup_script_00.R")
}else{
  source("/prj/aquacat/CodeABG/setup_script_00.R")
}

#ncname <- "run_hmfg2g/outputs/dmflow_RCM01_198012_201011_out.nc" #2GB

ND <- 10800 # Number of days



threshDayExcList <- readRDS(paste0(wd_id,"threshDayExcList2.rds"))
  #5 lists of NH lists

# Number of events
S <- sapply(threshDayExcList, function(l){length(l[[1]])})
for(i in 1:5){
  print(paste(threshName[i], "events per grid-cell:", S[i]))
}

thresMat <- readRDS(paste0(wd_id,"threshMat2.rds"))



```

## Find size of widespread inundation events.
```{r exceed, fig.width=10, fig.height=10}
# Number of sites exceeded for each day at each threshold
inunMat <- matrix(0, nrow=NT, ncol=ND)
inunDays <- matrix(0, nrow=NT, ncol=NH)

for(j in 1:NT){  # for each threshold value
  #print(threshName[j])
  for(k in 1:NH){ # at each river network gridcell
    tde_jk <- threshDayExcList[[j]][[k]]
    
    for(n in 1:length(tde_jk)){
      tde <- tde_jk[n] # which days was it exceeded
      inunMat[j,tde] <- inunMat[j,tde] + 1
      
    }
    
  }
}

rownames(inunMat) <- threshName

EventSizeSumm <- apply(inunMat, 1, function(v){
    quantile(v[v>0], probs=
               c(0.99,0.9,0.8,0.5,0.4, 0.3,0.2,0.1,0.01))
  })
```

```{r, fig.width=10, fig.height=10}
if(FALSE){
knitr::kable(EventSizeSumm/200) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

par(mgp=c(2,1,0), mar=c(3,3,1,0), mfrow=c(3,2))
for(j in 1:NT){
  hist(log(inunMat[j,inunMat[j,]>0]),
       main=paste("Threshold =", threshName[j]),
       xlab="log(Number of inundated cells)",
       ylab="Number of days")
  
}
par(mfrow=c(1,1))
}
```

### Number of days with widespread inundation
```{r, fig.width=10, fig.height=10}
if(FALSE){
# Percentage of inundated cells
wsBound <- c(0.05, 0.02, 0.01, 0.005, 0.001)
wsName <- c("pc5", "pc2", "pc1", "pc05", "pc01")
NW <- length(wsBound)

widespreadArray <- array(FALSE, dim=c(NT, ND, NW))
for(j in 1:NW){
  # Is there a widespread event on this day (at bound j)?
  widespreadArray[,,j] <- inunMat >= NH*wsBound[j] 
}
dimnames(widespreadArray) <- list(threshold = threshName,
                                  days=1:ND,
                                  inundation = c("pc5", "pc2", "pc1",
                                                 "pc05", "pc01"))

widespreadCount <- apply(widespreadArray, c(1,3), sum)



knitr::kable(widespreadCount) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
}
```

## Length of events
```{r}
if(FALSE){
eventLList <- vector("list",5)
names(eventLList) <- threshName
eventDayList <- vector("list", 5)
names(eventDayList) <- threshName

for(j in 1:5){
  eventLList[[j]] <- vector("list",5)
  names(eventLList[[j]]) <- wsName
  eventDayList[[j]] <- vector("list", 5)
  names(eventDayList[[j]]) <- wsName
  for(k in 1:5){
    eventGo <- 0
    eventL <- c()
    eventD <- c()
    for(i in 1:ND){
      if (widespreadArray[j, i, k]) {
       eventGo <- eventGo + 1
      }else{
        if (eventGo > 0){
         eventD <- c(eventD, i)
         eventL <- c(eventL, eventGo)
        #print(eventGo)
        }  
        eventGo <- 0
      }
    }
    eventLList[[j]][[k]] <- eventL
    eventDayList[[j]][[k]] <- eventD
  }
}
#save(eventLList, eventDayList,
#      file=paste0(wd,"CodeABG/InterimData/eventLists03.RDa"))
}
```

```{r fig.width=10, fig.height=10, echo=F}
if(FALSE){
load(paste0(wd, "CodeABG/InterimData/eventLists03.RDa"))
par(mfrow=c(5,5), mgp=c(2,1,0), mar=c(3,3,1,0))
for(j in 1:5){
  for(k in 1:5){
    ylab <- ifelse(k == 1, threshName[j], "")
    mainlab <- ifelse(j == 1, wsName[k], "")
    xlab <- ifelse(j==5, "Length in days", "")
    plot(table(eventLList[[j]][[k]]), ylab=ylab, main=mainlab,
         xlab=xlab,
         xlim=c(0,21), ylim=c(0,100), cex=0.7)
  }
}
}
```

```{r}
#load(paste0(wd,"CodeABG/InterimData/eventLists03.RDa"))
present <- readr::read_csv(paste0(data_wd,
                                  "TestData/present_returnlevels_POT2_pc05.csv"),
                           col_types = cols(
  eventNo = col_double(),
  loc = col_double(),
  Easting = col_double(),
  Northing = col_double(),
  thresh = col_double(),
  DayS = col_double(),
  val = col_double(),
  gpp = col_double(),
  ecdf = col_double(),
  gev = col_double()
))

present0 <- present %>%
  mutate(flood = val > thresh) %>%
  group_by(eventNo, DayS) %>%
  summarise(size = sum(flood)/19914) %>%
  ungroup() %>%
  arrange(desc(size))

netcdf <- nc_open(paste0(wd_id,"dmflow_timechunks.nc"))

which.min(present$gpp)

for(n in 1:5){
  event <- present0$eventNo[n]
  day <- present0$DayS[n]
  
  present_day <- present %>% dplyr::filter(eventNo == event)
  
  fl <- ncvar_get(netcdf, "dmflow", start=c(1,1,day), count=c(-1, -1, 1))
  
  flowM <- as.matrix(fl)
  
  s <- sum(flowM[!is.na(flowM)] > 0)
  
  Wdown <- present_day[which(present_day$val > present_day$thresh), ]
  print(dim(Wdown))
  WW <- present_day[which(present_day$val <= present_day$thresh), ]
  sw <- round(nrow(Wdown)/s, 2)*100
  
  # for (i in 1:nrow(WW)) {
  #   if(is.na(flowM[WW$Easting[i], WW$Northing[i]])) next
  #   if(!(flowM[WW$Easting[i], WW$Northing[i]] == -1)){
  #     flowM[WW$Easting[i], WW$Northing[i]] <- -0.5
  #   }
  # }
  
  flowM[rn[,1:2]] <- -0.5
  
  # for (j in 1:nrow(rn)) {
  #   flowM[rn[j,1],rn[j,2]] <- -0.5
  # }
  # 
  pp <- NA
  tp <- NA
  
  for (i in 1:nrow(Wdown)) {
    
    pp <- Wdown$gpp
    tp <- 1 - (1-pp)^360
    
    flowM[as.matrix(Wdown[,c("Easting","Northing")])] <-  1 / tp
    
  }
  
  
  flowR <- raster(flowM[,1000:1])
  
  flowN <- focal(flowR, w=matrix(1, 3, 3),
                 fun=function(x){if(!all(is.na(x))){max(x, na.rm=T)}else{return(NA)}})
  
  brks <- c(-1.01, -0.51, seq(0, max(70, na.rm=T), length.out=20))
  
  png(paste0("S:/Plots/exampleevent_day",day,"_size",nrow(Wdown), "_B.png"),
      res=300, width=100, height=100, units='mm', pointsize=10)
  par(mar=c(1,1,1,1), mgp=c(1,1,0))
  image.plot(as.matrix(flowM), x=0:700, y=0:1000, ylim=c(0,1000), zlim=c(-2,200),
             col=c("darkseagreen1", "darkseagreen2", topo.colors(19)),
             breaks=brks, asp=1,
             xlab="", ylab="", axes=F)
  
  pu <- par('usr')
  text(pu[1] + (pu[2] - pu[1])*0.9, pu[3] + (pu[4] - pu[3])*0.9,
       paste0("POT2 threshold\n", sw, "% inundation"),
       adj=c(1,0.5))
  
  dev.off()

}
```


