---
title: "Event Plotting - AQUACAT"
author: "UKCEH; Adam Griffin"
output:
  html_document: default
  pdf_document: default
---

This document investigates the different number and size of widespread events for different grid-cell threshold and inundation limits. This analysis is based on a 30-year "present-day" period of G2G outputs across Great Britain.

Outputs: "/exampleevent_DAY_INUN.png" plots

```{r setup, echo=F, message=F, warnings=F, errors=F}
library(ncdf4)
library(raster)
library(knitr)
library(kableExtra)
library(dplyr)


if(substr(osVersion,1,3) == "Win"){
  source("S:/CodeABG/setup_script_00.R")
}else{
  source("/prj/aquacat/CodeABG/setup_script_00.R")
}

##### DATA #####------------------------------------------------------------

threshDayExcList <- readRDS(paste0(data_wd, subfold,
                            "threshDayExcList_RCM", RCM, suffix, ".rds"))
#5 lists of NH lists

thresMat <- readRDS(paste0(data_wd, subfold, "threshMat_RCM",
                           RCM, suffix, ".rds"))


# Number of events
S <- sapply(threshDayExcList, function(l){length(l[[1]])})
for(i in 1:5){
  print(paste(threshName[i], "events per grid-cell:", S[i]))
}
```

# Data used and produced in previous scripts
```{r data}
# if(substr(osVersion,1,3) == "Win"){
#   wd <- "S:/"
# }else{
#   wd <- "/prj/aquacat/"
# }
# 
# ncname <- "run_hmfg2g/outputs/dmflow_RCM01_198012_201011_out.nc" #2GB
# 
# ND <- 10800 # Number of days
# 
# 
# rn <- read.csv(paste0(wd,"CodeABG/InterimData/hasData.csv"),
#                       stringsAsFactors=FALSE)
# NH <- nrow(rn)
# 
# 
# threshDayExcList <- readRDS(paste0(wd,
#                             "CodeABG/InterimData/threshDayExcList2.rds"))
#   #5 lists of NH lists
# 
# # Number of events
# S <- sapply(threshDayExcList, function(l){length(l[[1]])})
# for(i in 1:5){
#   print(paste(threshName[i], "events per grid-cell:", S[i]))
# }
# 
# thresMat <- readRDS(paste0(wd,"CodeABG/InterimData/threshMat2.rds"))
```

## Find size of widespread inundation events.
```{r exceed, fig.width=10, fig.height=10}
# Number of sites exceeded for each day at each threshold
inunMat <- matrix(0, nrow=NT, ncol=ND)
inunDays <- matrix(0, nrow=NT, ncol=NH)

for(j in 1:NT){  # for each threshold value
  #print(threshName[j])
  for(k in 1:NH){ # at each river network gridcell
    tde_jk <- threshDayExcList[[j]][[k]]
    
    for(n in 1:length(tde_jk)){
      tde <- tde_jk[n] # which days was it exceeded
      inunMat[j,tde] <- inunMat[j,tde] + 1
      
    }
    
  }
}

rownames(inunMat) <- threshName

EventSizeSumm <- apply(inunMat, 1, function(v){
    quantile(v[v>0], probs=
               c(0.99,0.9,0.8,0.5,0.4, 0.3,0.2,0.1,0.01))
  })

```

```{r, fig.width=10, fig.height=10}
knitr::kable(EventSizeSumm/200) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)

par(mgp=c(2,1,0), mar=c(3,3,1,0), mfrow=c(3,2))
for(j in 1:NT){
  hist(log(inunMat[j,inunMat[j,]>0]),
       main=paste("Threshold =", threshName[j]),
       xlab="log(Number of inundated cells)",
       ylab="Number of days")
  
}
par(mfrow=c(1,1))
```

### Number of days with widespread inundation
```{r, fig.width=10, fig.height=10}

# Percentage of inundated cells
wsBound <- c(0.05, 0.02, 0.01, 0.005, 0.001)
wsName <- c("pc5", "pc2", "pc1", "pc05", "pc01")
NW <- length(wsBound)

widespreadArray <- array(FALSE, dim=c(NT, ND, NW))
for(j in 1:NW){
  # Is there a widespread event on this day (at bound j)?
  widespreadArray[,,j] <- inunMat >= NH*wsBound[j] 
}
dimnames(widespreadArray) <- list(threshold = threshName,
                                  days=1:ND,
                                  inundation = c("pc5", "pc2", "pc1",
                                                 "pc05", "pc01"))

widespreadCount <- apply(widespreadArray, c(1,3), sum)



knitr::kable(widespreadCount) %>%
  kable_styling(bootstrap_options = "striped", full_width = F)
```

## Length of events
```{r}
eventLList <- vector("list",5)
names(eventLList) <- threshName
eventDayList <- vector("list", 5)
names(eventDayList) <- threshName

for(j in 1:5){
  eventLList[[j]] <- vector("list",5)
  names(eventLList[[j]]) <- wsName
  eventDayList[[j]] <- vector("list", 5)
  names(eventDayList[[j]]) <- wsName
  for(k in 1:5){
    eventGo <- 0
    eventL <- c()
    eventD <- c()
    for(i in 1:ND){
      if (widespreadArray[j, i, k]) {
       eventGo <- eventGo + 1
      }else{
        if (eventGo > 0){
         eventD <- c(eventD, i)
         eventL <- c(eventL, eventGo)
        #print(eventGo)
        }  
        eventGo <- 0
      }
    }
    eventLList[[j]][[k]] <- eventL
    eventDayList[[j]][[k]] <- eventD
  }
}
# save(eventLList, eventDayList,
#       file=paste0(wd,"CodeABG/InterimData/eventLists03.RDa"))
```

```{r fig.width=10, fig.height=10, echo=F}
#load(paste0(wd, "CodeABG/InterimData/eventLists03.RDa"))
par(mfrow=c(5,5), mgp=c(2,1,0), mar=c(3,3,1,0))
for(j in 1:5){
  for(k in 1:5){
    ylab <- ifelse(k == 1, threshName[j], "")
    mainlab <- ifelse(j == 1, wsName[k], "")
    xlab <- ifelse(j==5, "Length in days", "")
    plot(table(eventLList[[j]][[k]]), ylab=ylab, main=mainlab,
         xlab=xlab,
         xlim=c(0,21), ylim=c(0,100), cex=0.7)
  }
}
dev.off()
table(eventLList[[2]][[4]])
png("./eventLengths.png", width=120, height=120, units="mm", res=240)
par(mgp=c(2,1,0), mar=c(3,3,1,0))
    ylab <- "Number of events"
    mainlab <- "Minimum 0.5% coverage"
    xlab <- "Length in days"
    plot(table(eventLList[[2]][[4]]), ylab=ylab, main=mainlab,
         xlab=xlab,
         xlim=c(0,35), ylim=c(0,150), cex=0.7, type='o')
dev.off()
```

```{r}
#load(paste0(wd,"CodeABG/InterimData/eventLists03.RDa"))
# qv <- c()
# 
# for(qi in quantile(inunMat[4,inunMat[4,]>0],
#                    probs=c(0.5,0.55,0.6,0.65,0.7,0.75,0.8,0.85))){
#   print(qi)
#   qv <- c(qv,which.min(abs(inunMat[4,] - qi)))
# }
# 
# netcdf <- nc_open(ncname)
# var <- "dmflow"
# for(i in 1:length(qv)){
# 
#   day <- qv[i]
#   #flow <- raster(ncname_win, layer=day)
#   fl <- ncvar_get(netcdf, var, start=c(1,1,day), count=c(-1, -1, 1))
#   flowM <- as.matrix(fl)[,1000:1]
#   
#   s <- sum(flowM[!is.na(flowM)] > 0)
#   
#   Wdown <- which(flowM > threshgrid, arr.ind=T)
#   print(dim(Wdown))
#   WW <- which(flowM <= threshgrid, arr.ind=T)
#   sw <- round(length(which(flowM > threshgrid))/s, 2) * 100 # % inundation
#   
#   for(i in 1:nrow(WW)){
#     if(is.na(flowM[WW[i,1], WW[i,2]])) next
#     if(!(flowM[WW[i,1], WW[i,2]] == -1)){
#       flowM[WW[i,1], WW[i,2]] <- -0.5
#     }
#   }
#   
#   flowM <- focal(as.raster(flowM), w=matrix(1,3,3),
#                  fun=function(x){if(!all(is.na(x))){max(x, na.rm=T)}else{return(NA)}},
#                  na.rm=T)
#   
#   brks <- c(-1.01, -0.51, seq(0, max(1500, na.rm=T), length.out=20))
#   
#   png(paste0("./Aexampleevent_",extremes$Day[w[k]],"_",extremes$Inun[w[k]], ".png"),
#       res=300, width=70, height=70, units='mm', pointsize=9)
#   par(mar=c(3,3,1,1), mgp=c(2,1,0))
#   image.plot(flowM, x=0:700, y=0:1250, ylim=c(0,1250), zlim=c(-2,1500),
#              col=c("grey90", "grey90", heat.colors(19)), breaks=brks, asp=1,
#              xlab="Easting", ylab="Northing")
#   
#   #pu <- par('usr')
#   
#   #text(pu[1] + (pu[2]-pu[1])*0.9, pu[3] + (pu[4] - pu[3])*0.9,
#   #     paste0("POT5 threshold\n", sw, "% inundation"),
#   #     adj=c(1,0.5))
#   dev.off()
# }
```