---
title: "texmex scratch"
author: "UKCEH; Adam Griffin"
date: "12/02/2020"
output: html_document
---

# AquaCAT, Project 07441

This document investigates the `texmex` package, the netCDF files coming out of 
the G2G modelling, and what needs wrangling to get the data in a reasonable shape.
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

### PACKAGES
library(texmex)
library(ncdf4)
library(fields)
```


### Adjusted texmex functions
These functions allow the printing of one or two plots, not all the pairwise plots.
```{r func, include=FALSE}
plottexmex <- function (x, plots = "gpd", main = "", plotnum=NULL, ...) {
  if (casefold(plots) == "gpd") {
      which <- 1
  }
  else {
      which <- 2
  }
  d2 <- dim(x$boot[[1]][[which]])
  pointEst <- x$simpleDep
  condVar <- names(x$simpleMar$data)[x$which]
  margins <- x$margins
  x <- x$boot
  co <- unlist(lapply(x, function(z, wh) z[[wh]], wh = which))
  co <- array(co, dim = c(d2[1], d2[2], length(co)/prod(d2)))
  lco <- list(length = prod(d2))
  for (i in 1:d2[2]) {
      for (j in 1:d2[1]) {
          lco[[j + d2[1] * (i - 1)]] <- co[j, i, ]
      }
  }
  cn <- colnames(x[[1]][[which]])
  rn <- rownames(x[[1]][[which]])
  if (which == 2) {
      cn <- paste(cn, "|", condVar)
  }
  labs <- paste(rep(rn, length(cn)), rep(cn, each = switch(which, 
      2, 6)), sep = "  ")
  fun <- function(X, z, label, ...) {
      hist(z[[X]], prob = TRUE, xlab = label[X], main = main, 
          ...)
      lines(density(z[[X]], n = 100))
      invisible()
  }
  if (which == 1) {
      if(is.null(plotnum)){
        plotnum <- 1:d2[2]
      }
      lapply(plotnum, fun, z = lco, label = labs, ...)
  }
  if (which == 2) {
      fun <- function(X, z, label, ...) {
          offset <- (X - 1) * 6
          plot(lco[[offset + 1]], lco[[offset + 2]], xlab = labs[offset + 
              1], ylab = labs[offset + 2], main = main, ...)
          points(pointEst[1, X], pointEst[2, X], pch = "@", 
              col = 2)
          if (margins[[1]] == "gumbel") {
              plot(lco[[offset + 3]], lco[[offset + 4]], xlab = labs[offset + 
                3], ylab = labs[offset + 4], main = main, ...)
              points(pointEst[3, X], pointEst[4, X], pch = "@", 
                col = 2)
          }
      }
      if(is.null(plotnum)){
        plotnum <- 1:d2[2]
      }
      lapply(plotnum, fun, z = lco, label = labs, ...)
  }
  invisible()
}


plotpredmex <- function(x, pch = c(1, 3, 20), col = c(2, 8, 3), cex = c(1, 
    1, 1), ask = TRUE, plotnum=NULL, ...){
  d <- dim(x$data$simulated)[[2]] - 1
  if (prod(par("mfrow")) < d) {
      if (ask) {
          op <- par(ask = TRUE)
          on.exit(par(op))
      }
  }
  xdat <- x$data$real[, 1]
  upts <- seq(from = 0.001, to = 1 - 1e-04, len = 100)
  xpts <- texmex:::revTransform(upts, data = x$data$real[, 1],
                                qu = mean(x$data$real[, 1] < x$mth[1]),
                                th = x$mth[1],
                                sigma = x$gpd.coef[3, 1],
                                xi = x$gpd.coef[4, 1])
  if(is.null(plotnum)){
    plotnum <- 2:(dim(x$data$real)[[2]])
  }
  for (i in plotnum) {
      ydat <- x$data$real[, i]
      xlimits <- range(xdat, x$data$simulated[, 1])
      ylimits <- range(ydat, x$data$simulated[, i])
      plot(xdat, ydat, xlim = xlimits, ylim = ylimits,
          xlab = names(x$data$simulated)[1], 
          ylab = names(x$data$simulated)[i], type = "n", 
          ...)
      points(x$data$simulated[x$data$CondLargest, 1],
             x$data$simulated[x$data$CondLargest, i],
             col = col[3], pch = pch[3], cex = cex[3])
      points(x$data$simulated[!x$data$CondLargest, 1],
             x$data$simulated[!x$data$CondLargest, i],
             col = col[2], pch = pch[2], cex = cex[2])
      points(xdat, ydat, pch = pch[1], col = col[1], cex = cex[1])
      abline(v = x$data$pth, lty = 2, col = 3)
      ypts <- texmex:::revTransform(upts, data = x$data$real[, i],
                           qu = mean(x$data$real[, i] < x$mth[i]),
                           th = x$mth[i],
                           sigma = x$gpd.coef[3, i],
                           xi = x$gpd.coef[4, i])
      lines(xpts, ypts, col = 3)
  }
  invisible()
}
```

## Data
The data will come in 20-30 year periods on a daily time step (with possible difference in days/year). Data is in netCDF format, and is currently hosted on the linux network.
```{r data}
ncname_lin <-"/prj/ResilRiskInds/hmfg2g_runs/baseline_qx_setting/dmflow_out.nc"
ncname_win <- "K:/hmfg2g_runs/baseline_qx_setting/dmflow_out.nc"  
  # This file is ~36GB on the linux server.
ST <- Sys.time()
ncin <- nc_open(ncname_win)
print(Sys.time() - ST)
print(ncin)
```

Here we just take a small sample from the dataset (25*25 gridpoints for 2000 days) to take a look. `NA` is sea pixels, `-1` is not on the river network.
```{r extraction}
istart <- 390
Di <- 25
jstart <- 400
Dj <- 25
tstart <- 101
Dt <- 2000

ST <- Sys.time()
ncflow <- ncvar_get(ncin, varid="dmflow",
                    start=c(istart,jstart,101), count=c(Di,Dj,Dt))
print(Sys.time() - ST)
# for Di = 25, Dj = 25, Dt = 2000, ncflow is ~10MB

for(i in 1:5){
  v <- as.vector(ncflow[,,i])
  print(paste("Range:", max(v[!is.na(v) & v > -1]), 
        min(v[!is.na(v) & v > -1])))
  print(paste("Number of -1s:", sum(v[!is.na(v)]==-1)))
  print(paste("Number of NAs:", sum(is.na(v))))
}
image.plot(ncflow[,,1])

ST <- Sys.time()
ncWide <- ncvar_get(ncin, varid="dmflow", start=c(1, 1, tstart),
                    count=c(-1, -1, 1))
print(Sys.time() - ST)

v <- as.vector(ncWide)
print(paste("Range:", max(v[!is.na(v) & v > -1]), 
        min(v[!is.na(v) & v > -1])))
print(paste("Number of -1s:", sum(v[!is.na(v)]==-1)))
print(paste("Number of NAs:", sum(is.na(v))))

image.plot(ncWide[,dim(ncWide)[2]:1])
```

## Event extraction
This will either be much more or much less in depth for the final dataset.
```{r eventextract}
HasData <- which(apply(ncflow, c(1,2),
                       function(v){sum(v[which(!is.na(v))] > -1) == Dt}),
                 arr.ind=T)
# HasData is important for gluing the events back in at the other end of the
# pipeline.

ncData <- matrix(NA, ncol=nrow(HasData), nrow=Dt)
for(i in 1:nrow(HasData)){
  ncData[,i] <- ncflow[HasData[i,1], HasData[i,2],]
}
```

For this, it is worth noting that for ` is.na(v) & v > -1` we have `FALSE & NA == FALSE`.

## Using texmex
This section gives a quick overview of the main functions needed from texmex.
```{r texmex}
ST <- Sys.time()
  mmex <- mex(ncData, mqu=.7, penalty="none", dqu=.7, which=2)
print(Sys.time() - ST)

ST <- Sys.time()
  myboot <- bootmex(mmex, R=10)  # R=10 is quite low.
print(Sys.time() - ST)

plottexmex(myboot, plotnum=3:6)

ST <- Sys.time()
mypred <- predict(myboot,  pqu=.99)
print(Sys.time() - ST)
plotpredmex(mypred, plotnum=3:6)


summary(mypred, probs = c(0.025, 0.5, 0.975))

MGPD <- migpd(ncData[,1:6], mqu=.7, penalty="none", maxit=1000)

mexdep <- mexDependence(MGPD, which=1, dqu=.7, margins="gumbel")
#mall <- mexAll(ncData[,1:6], mqu=0.8, dqu=0.8)

res <- lapply(1:6, function(i) {
    mex(ncData[,1:6], which = i, mqu = 0.8, dqu = 0.8)
})
names(res) <- names(data)
oldClass(res) <- "mexList"


mmc <- mexMonteCarlo(500, res)
pairs(mmc$MCsample[,1:3])
```

Not sure what this means, but this is the text from plotting mex predict objects.

The plot method for class "predict.mex" displays both the original data and the simulated data generated above the threshold for prediction; it shows the threshold for prediction (vertical line) and also the curve joining equal quantiles of the marginal distributions – this is for reference: variables that are perfectly dependent will lie exactly on this curve. Original data are shown with one plotting character and simulated data with another; colours of simulated point distinguish those points which have the conditioning variable as the largest (on a quantile scale) or not the largest.